---
title: "PSY 8712 Week 8 Project"
author: "Michael Hazboun"
date: "`r Sys.Date()`"
output: 
  html_document:
    df_print: paged
---

I finished this and noticed that you wanted 1 to 2 sentence explanations for why we chose to do what we did. I used much more than that to start, so for the full version [go here](https://docs.google.com/document/d/1hO2VGmAc63v3pOvx9EORhB7ONFAcy36gHcczCAgYwTc/edit?usp=sharing)

**Reproducible Image and Online Resources:**

An image of this project as of *`r Sys.Date()`* can be accessed by [clicking this link](link). COME BACK AND PUT LINK
An interactive web app is available by [clicking this link instead](link). COME BACK AND PUT LINK

**Script Settings and Resources**

```{r Script Settings and Resources, echo=FALSE}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)

```

**Data Import and Cleaning**

Imported and cleaned the data: factorized gender, reverse coded q5 and made two new variables, the mean for Q1:6 and the mean for Q8:10. I didn't change anything else because I didn't want to make any assumptions on this dataset based off of our previous homeworks (we might be in a different world where q6 wasn't used as a manipulation check...)
```{r Data Import and Cleaning}
week8_tbl <- read_csv("../data/week3.csv", col_names = T) %>%
  mutate(gender = factor(gender, levels=c("M","F"), labels = c("Male","Female"))) %>%
  mutate(q5=6-q5)%>%
  rowwise()  %>%
  mutate(mq1_6= mean(c(q1,q2,q3,q4,q5,q6), na.rm = T)) %>%  # I tried using q1:q6, but when I was checking the responses, it wasn't right, it was giving me different answers for each line, but not the right one..
  mutate(mq8_10= mean(c(q8,q9,q10), na.rm = T))

```

**Visualization**

I hid the code using echo, hid the message using message and made a plot using ggplot, geom_point and geom_smooth. I used these methods because they were the easiest and most intuitive to me. 
```{r Visualization, echo=FALSE, message=FALSE}
week8_tbl %>%
  select(q1:q6)

week8_tbl %>%
  ggplot(aes(x=mq1_6,y=mq8_10))+
  geom_point() +
  geom_smooth( method = "lm",color="purple")+
  labs(x= "Mean of Q1 through Q6", y= "Mean of Q8 through Q10")

```

**Analysis**

I calculated the correlation, pulled the pvalue and correlation out of the output and rounded both values with round() and removed the leading zeros with str_remove. This was the easiest way I could think of to remove the leading zeros. (Also hid the code using echo=F)
```{r Analysis, echo=FALSE}
wow_correlation<-cor.test(week8_tbl$mq1_6,week8_tbl$mq8_10)
pvalue <-str_remove(round(wow_correlation$p.value,2) ,"^0")
wow_correlation
pretty_cor<- str_remove(round(wow_correlation$estimate,2),"^0")
```

I observed a correlation of `r pretty_cor` between the mean of questions one through six and the mean of question eight through  ten. The associated P values was rough `r pvalue`, assuming an alpha of 0.05, we fail to reject the null hypothesis, that the correlation between the means is actually 0, because the p value is larger than our alpha.

**Data Export**

I used saveRDS to same the file in the shiny folder and only included relevant variables.
```{r Data Export}
week8_tbl %>%
  select(timeEnd,gender,mq1_6,mq8_10) %>%
  saveRDS("../shiny_week8/data.rds")
```